% AJAX
\newglossaryentry{AJAX}{name={AJAX},text=AJAX,
description={Asynchronous JavaScript and XML: A method for the browser to interface with the server without reloading the page, so as to create a seamless user experience.}}

% API
\newacronym[description={\glslink{apig}{Application Protocol Interface}}]{API}{API}{Application Protocol Interface}

\newglossaryentry{apig}{name=\glslink{API}{Application Protocol Interface},text=Application Protocol Interface,
description={An interface for a piece of software that enables other pieces of software to use its functionality.}}

% CBA
\newacronym[description={Cost-Benefit Analysis}]{CBA}{CBA}{Cost-Benefit Analysis}

% CDF and PDF
\newacronym[description={Cumulative Distribution Function}]{cdf}{cdf}{Cumulative Distribution Function}

\newacronym[description={Probability Density Function}]{pdf}{pdf}{Probability Density Function}

% DRY
\newacronym[description={Don't Repeat Yourself}]{DRY}{DRY}{Don't Repeat Yourself}

% Get
\newglossaryentry{get}{name=GET, description={A GET request method is a way for the browser to ask for data from the server. The data is requested with URL parameters in the form "?a=1\&b=2}}

% GPL
\newacronym[description={GNU General Public License}]{GPL}{GPL}{GNU General Public License}

% GWT
\newacronym[description={Google Web Toolkit}]{GWT}{GWT}{Google Web Toolkit}

% HTTP
\newglossaryentry{HTTP}{name=HTTP, description={Hypertext Transfer Protocol is the protocol used by the Internet to transfer information from a server to a browser and back again.}}

% JQuery
\newglossaryentry{jquery}{name=JQuery, description={A JavaScript library which can handle animations and AJAX.}}

% MVT
\newacronym[description={Model-View Template}]{MVT}{MVT}{Model-View Template}

% OO
\newacronym[description={Object-Oriented}]{OO}{OO}{Object-Oriented}

% ORM
\newacronym[description={\glslink{ormg}{Object Relational Mapping}}]{ORM}{ORM}{Object Relational Mapping}

\newglossaryentry{ormg}{name=\glslink{ORM}{Object Relational Mapping},text=Object Relational Mapping,
description={An interface between objects in programming code and database tables on a server.}}

% OSM
\newacronym[description={OpenStreetMap}]{OSM}{OSM}{OpenStreetMap}

% Post
\newglossaryentry{post}{name=POST, description={A POST request method is a way for the browser to send data to the server. The data is not seen by the user.}}
% Regex
\newacronym[description={\glslink{regexg}{Regular Expression}}, \glsshortpluralkey={regexes}]{regex}{regex}{Regular Expression}

\newglossaryentry{regexg}{name=\glslink{regex}{Regular Expression},text=Regular Expression,
description={A regular expression defines a pattern of characters which can be used by a regex matcher to search a string and determine if the string contains substrings which fit the pattern.}}

% RSS
\newacronym[description={\glslink{rssg}{Really Simple Syndication}}]{RSS}{RSS}{Really Simple Syndication}

\newglossaryentry{rssg}{name=\glslink{RSS}{Really Simple Syndication},text=Really Simple Syndication,
description={A method of publishing frequently updated web pages and allowing users to subscribe to the content.}}

% Session
\newglossaryentry{session}{name=Session, description={A session is a way for the server to store information specific to the user currently using the website.}}

% SMS Gateway
\newglossaryentry{smsg}{name=SMS Gateway, description={A paid-for service which allows SMS messages to be sent through a website, usually using an email address.}}

% Stack overflow
\newglossaryentry{so}{name=Stack Overflow, text={Stack Overflow\cite{stackoverflow}}, description={An online community for users to post questions with programming problems and other users to answer them.}}

% WBG
\newacronym[description={World Bank Group}]{WBG}{WBG}{World Bank Group}
